Identifying regime transitions for water governance at a basin scale

### 2023-05-22 paper/diff/v-8.2.1.tex
fix(paper): :memo: 调整并更新数据开源表述

	For calculating IWGI, three datasets were used: reservoirs, measured runoff, and water uses.
	The reservoir dataset was collected by~\citeA{wang2019c}, which introduced includes the significant new reservoirs built in the YRB since 1949 (Accessible with reasonable request).
	Among all the reservoirs, YRCC labelled the ``major reservoirs'' which were constructed mainly for regulating and managing (see \url{http://www.yrcc.gov.cn/hhyl/sngc/}).
	In addition, annual measured runoff data was collected from the Yellow River Sediment Bulletin (\url{http://www.yrcc.gov.cn/nishagonggao/}) and four controlling stations are measuring different reaches of the Yellow River (see Supporting Informations Section~S1).
	The water resources use dataset was from National Long-term Water Use Dataset of China (NLWUD) published by \citeA{zhou2020}, which includes water uses, water-consuming economic variables, and water use intensities by sectors the prefectures level.
	We determined the prefectures belong to the YRB by filtering the NLWUD dataset with a threshold of $95\%$ intersected area.

@@

\section*{Open Research Section}
All the used datasets and their links are detailed described in the Section~\ref{sec:datasets}.

@@

\bibliography{../mybibtex.bib}

>>>>

	For calculating IWGI, three datasets were used: reservoirs, measured runoff, and water uses.
	The reservoir dataset was collected by~\citeA{wang2019c}, which introduced includes the significant new reservoirs built in the YRB since 1956.
	Among all the reservoirs, YRCC labelled the ``major reservoirs'' which were constructed mainly for regulating and managing (see \url{http://www.yrcc.gov.cn/hhyl/sngc/}).
	In addition, annual measured runoff data was collected from the Yellow River Sediment Bulletin (\url{http://www.yrcc.gov.cn/nishagonggao/}) and four controlling stations are measuring different reaches of the Yellow River (see Supporting Informations Section~S1).
	The water resources use dataset was from National Long-term Water Use Dataset of China (NLWUD) published by \citeA{zhou2020}, which includes water uses, water-consuming economic variables, and water use intensities by sectors the prefectures level.
	We determined the prefectures belong to the YRB by filtering the NLWUD dataset with a threshold of $95\%$ intersected area.

@@

\section*{Open Research Section}
Data deposition: All data used or analyzed during this study, including the reservoirs dataset, measured runoff, water uses datasets, laws, and big events have been deposited at \url{https://doi.org/10.5281/zenodo.7955501}~\cite{shuang_song_2023_7955501}.

@@

\bibliography{../v-8.2.1.bib}

### 2023-05-22 paper/main/manuscript.tex
fix(paper): :memo: 调整并更新数据开源表述

\section*{Open Research Section}
All the used datasets and their links are detailed described in the Section~\ref{sec:datasets}.
% The National Long-term Water Use Dataset of China (NLWUD) dataset within the Yellow River Basin uploaded.

>>>>

\section*{Open Research Section}
Data deposition: All data used or analyzed during this study, including the reservoirs dataset, measured runoff, water uses datasets, laws, and big events have been deposited at \url{https://doi.org/10.5281/zenodo.7955501}~\cite{shuang_song_2023_7955501}.
